Some examples of the use of Aa relative to C

### 2021-10-24 v2/Ahir-asm/devel/docs/AaExamples.tex

       $if (J < 31) $then
           $place[loopback]
       $endif 
   }  (n_min_val => MINVAL n_min_index => MININDEX)

@@

   // read matrix
   for (I = 0; I < 32; I++) {
      for (J = 0; J < 32; J++) {
        A[I][J] = read_uint32("input_pipe");
      }
   }
   // matrix multiply
   for (I = 0; I < 32; I++) {
      for (J = 0; J < 32; J++) {
         uint32_t tmp = 0;
         for (K = 0; J < 32; J++) {
            tmp += A[I][K]*A[K][J];
         }
         ASQ[I][J] = tmp;
      }
   }
   // send out.
   for (I = 0; I < 32; I++) {
      for (J = 0; J < 32; J++) {
        write_uint32("output_pipe", A[I][J]);
      }
   }
}
\end{verbatim}

>>>>

       $if (J < 31) $then
           $place[min_loopback]
       $endif 
   }  (n_min_val => MINVAL n_min_index => MININDEX)

@@

   // read matrix
   for (I = 0; I < 32; I++) {
      for (J = 0; J < 32; J++) {
        A[I][J] = read_uint32("input_pipe");
      }
   }
   // matrix multiply
   for (I = 0; I < 32; I++) {
      for (J = 0; J < 32; J++) {
         uint32_t tmp = 0;
         for (K = 0; J < 32; J++) {
            tmp += A[I][K]*A[K][J];
         }
         ASQ[I][J] = tmp;
      }
   }
   // send out.
   for (I = 0; I < 32; I++) {
      for (J = 0; J < 32; J++) {
        write_uint32("output_pipe", ASQ[I][J]);
      }
   }
}
\end{verbatim}
